Age-related changes in plant growth and traits

### 2016-09-09 scripts/Accessory_figs_20160905.Rmd
continued work on all different parts of Accessory Costs manuscript

@@

@@

@@

#Table 1 showing accessory cost values for the species
```{r}
acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,embryo_endo_size,repro_inv_per_seed,seedset,prop_failure,prop_prepollen_vs_RE, prop_dispersal_vs_RE,prop_embryo_endo_vs_RE,seed_costs,prop_prepollen_costs,prop_postpollen_costs)
acc_costs_spp$species <- labels.spp.full()
acc_costs_spp_format <- acc_costs_spp
for (i in c("embryo_endo_size","repro_inv_per_seed","seedset","prop_failure","prop_prepollen_vs_RE","prop_dispersal_vs_RE","prop_embryo_endo_vs_RE","seed_costs","prop_prepollen_costs","prop_postpollen_costs")) {
  acc_costs_spp_format[[i]] <- round(acc_costs_spp_format[[i]],digits=3)
}

@@

@@

@@

@@

acc_by_species$variable = c("total accessory costs","pre-pollination costs","provisioning costs", "failed tissues costs","failed pre-pollination costs","failed provisioning costs")

@@

#Table 3.correlations between repro inv and propagule inv by species
```{r}
yvar <- "repro_inv"
xvar <- "propagule_inv"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

write.csv(results, file="figs2/Accessory_Costs/Table03_propagule_invest_vs_repro_inv.csv",row.names=FALSE)
```

#Table 4. correlations with total repro inv
```{r}
results <- as.data.frame(matrix(vector(), 0, 9,
                dimnames=list(c(), c("xvar","variable","r2","pval","Slope","Slope_lowCI","Slope_highCI","Int","Slope_test_p"))),
                stringsAsFactors=F)

@@

write.csv(results, file="figs2/Accessory_Costs/Table04_correlations_with_repro_inv.csv",row.names=FALSE)
```

#Figure 2. Scaling of accessory costs versus weight of embryo + endosperm, by species
```{r}
win.metafile("figs2/Accessory_Costs/Figure04_embryo_size_acc_cost_correlations.wmf", height=9, width=10)
plot

par(mfrow=c(2,2), cex=1, omi=c(1,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
options(scipen = 5)

plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.02,5000),ylim=c(.004,.5),cex=1.5,xaxt="n",xlab="",ylab="")
mod <- sma(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy", method="OLS")
y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
text((10^(0.99*(par("usr")[2]-par("usr")[1])+par("usr")[1])),(10^(0.97*(par("usr")[4]-par("usr")[3])+par("usr")[3])),paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
axis(1, at=c(0.1,10,1000), labels=c("","",""),cex.axis=1)
mtext("seed set",2,line=2.3)
extra.bottom.left.logxy("a",2,1.2)

plot((scaled_seed_count)~(embryo_endo_size),SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.02,5000),ylim=c(1e-4,1000),yaxt="n",xaxt="n",ylab="")
points(scaled_bud_count~embryo_endo_size,SummaryInd,pch=21,col=col.spp(species))
#points(scaled_failure_count~embryo_endo_size,SummaryInd,pch=2,col=col.spp(species))
axis(2, at=c(0.0001,0.01,1,100), labels=c(0.0001,0.01,1,100),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c("","",""),cex.axis=1)
extra.bottom.left.logxy("b",2,1.2)
mtext("count, scaled to plant size",2,line=2.3)

mod1 <- sma(scaled_seed_count~embryo_endo_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="OLS")
mod2 <- sma(scaled_bud_count~embryo_endo_size,data=subset(SummaryInd,scaled_bud_count!=0),log="xy",slope=-1,method="OLS")
mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")

@@

plot(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.02,5000), ylab="",xlab="",cex=1.5)
y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
mod <- sma(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="OLS")
#abline(mod$groupsummary["Int"][[1]],1,lty=2)
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
mtext("pollen attraction costs (mg/seed)",2,line=2.3)
line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
line_function_log_xy_zero(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
extra.top.left.logxy("c",2,1.2)

plot(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.02,5000), ylab="",xlab="",cex=1.5)
y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_all_per_seed,SummarySpp[["se"]]$prepollen_costs)
mod <- sma(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="OLS")
line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
line_function_log_xy_zero(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
mtext("provisioning costs (mg/seed)",2,line=2.3)
extra.top.left.logxy("d",2,1.2)

>>>>

plot(scaled_seed_count ~ scaled_bud_count, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),xlim=c(.1,5000),ylim=c(0.001,50))
mod <- sma(scaled_seed_count ~ scaled_bud_count, SummarySpp[["mean"]],log="xy",slope=1,method="OLS")
summary(mod)
line_function_log_xy(SummarySpp[["mean"]]$scaled_bud_count,mod,1)
line_function_log_xy_zero(SummarySpp[["mean"]]$scaled_bud_count,mod,1)

plot(scaled_bud_count ~ seedset, SummarySpp[["mean"]],log="y",pch=16,col=col.spp(species))

@@

#proportion energy invested in accessory tissues unrelated to seedsize
mod <- sma(seed_size ~ prop_accessory_ee, data=subset(SummarySpp[["mean"]],species!="BAER"),method="OLS", log="y",slope.test=1)
summary(mod)
plot(seed_size ~ prop_accessory_ee, SummarySpp[["mean"]],log="y",pch=16,col=col.spp(species))

@@

#seedset by pollen attraction
mod <- sma(prop_prepollen_costs~seedset,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="OLS")
summary(mod)

@@

#Table 1 showing accessory cost values for the species
```{r}
acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,embryo_endo_size,seedset,repro_inv_per_seed,prop_failure,prop_prepollen_vs_RE, prop_dispersal_vs_RE,prop_embryo_endo_vs_RE,seed_costs,prop_prepollen_costs,prop_postpollen_costs,embryo_endo_size,pack_disp_costs,prepollen_costs,failure_inv,repro_inv,seed_count)
acc_costs_spp$species <- labels.spp.full()
acc_costs_spp_format <- acc_costs_spp
for (i in c("embryo_endo_size","seedset","repro_inv_per_seed","prop_failure","prop_prepollen_vs_RE","prop_dispersal_vs_RE","prop_embryo_endo_vs_RE","seed_costs","prop_prepollen_costs","prop_postpollen_costs")) {
  acc_costs_spp_format[[i]] <- round(acc_costs_spp_format[[i]],digits=3)
}

for (i in c("prop_failure","prop_prepollen_vs_RE","prop_dispersal_vs_RE","prop_embryo_endo_vs_RE","prop_prepollen_costs","prop_postpollen_costs")) {
  acc_costs_spp_format[[i]] <- round(100*acc_costs_spp_format[[i]],digits=1)
}

@@

#Table 1. color dots
```{r}
win.metafile("figs2/Accessory_Costs/Table01_dots.wmf", height=3, width=.2)
plot

par(mfrow=c(1,1), cex=1, omi=c(.01,.01,.01,.01), mai=c(.01,.01,.01,.01)) 
dots <- dplyr::select(SummarySpp[["mean"]],species)
dots$x <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1)
dots$y <- c(28,26,24,22,20,18,16,14,12,10,8,6,4,2)
plot(y~x,dots,cex=1.5,pch=16,xlab="",ylab="",xaxt="n",yaxt="n",col=col.spp(dots$species),bty="n",xlim=c(0.8,1.2),ylim=c(1.8,28.2))

@@

plot(seed_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="seed costs (mg/seed)",xlab="",cex=1.5)
y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seed_costs,SummarySpp[["se"]]$seed_costs)
slopes <- sma(seed_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,lty=2)
acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

@@

plot(prepollen_all_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="all pre-pollination costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_all_per_seed,SummarySpp[["se"]]$prepollen_all_per_seed)
slopes <- sma(prepollen_all_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,lty=2)
acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

@@

acc_by_species$variable = c("total accessory costs","seed costs","pollen attraction costs","provisioning costs", "failed tissues costs","all pre-pollen costs per seed","failed pre-pollination costs","failed provisioning costs")

@@

#Table Supplementary.correlations between repro inv and propagule inv by species
```{r}
yvar <- "repro_inv"
xvar <- "propagule_inv"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- fit$groupsummary
results$r2 <- format(results$r2,digits=2)
results$pval <- format(results$pval,digits=3)
acc_slopes <- dplyr::select(results,group,n,r2,pval)
names(acc_slopes) <- c("species","n_propagule","r2_propagule","p_propagule")

yvar <- "repro_inv"
xvar <- "flower_inv"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- fit$groupsummary
results$r2 <- format(results$r2,digits=2)
results$pval <- format(results$pval,digits=3)
acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
names(acc_slopes2) <- c("species","n_flower","r2_flower","p_flower")
acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")

write.csv(acc_slopes, file="figs2/Accessory_Costs/Table_S3_propagule_invest_vs_repro_inv.csv",row.names=FALSE)
```

#Table 3. correlations with total repro inv
```{r}
results <- as.data.frame(matrix(vector(), 0, 9,
                dimnames=list(c(), c("xvar","variable","r2","pval","Slope","Slope_lowCI","Slope_highCI","Int","Slope_test_p"))),
                stringsAsFactors=F)

@@

write.csv(results, file="figs2/Accessory_Costs/Table03_correlations_with_repro_inv.csv",row.names=FALSE)
```

plot(scaled_seed_count~prop_prepollen_costs,SummarySpp[["mean"]],pch=16,log="y",col=col.spp(species))
points(scaled_bud_count~prop_prepollen_costs,SummarySpp[["mean"]],pch=21,col=col.spp(species))
#points(scaled_failure_count~embryo_endo_size,SummaryInd,pch=2,col=col.spp(species))
axis(2, at=c(0.0001,0.01,1,100), labels=c(0.0001,0.01,1,100),cex.axis=1)
axis(1, at=c(0.01,1,100), labels=c("","",""),cex.axis=1)
mtext("count, scaled to plant size",2,line=2.3)
mod1 <- sma(scaled_seed_count~prop_prepollen_costs,data=subset(SummarySpp[["mean"]],scaled_seed_count!=0),log="y",slope=-1,method="OLS")
mod2 <- sma(scaled_bud_count~prepollen_costs,data=subset(SummarySpp[["mean"]],scaled_bud_count!=0),log="xy",slope=3.23,method="OLS")
mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")

@@

summary(mod1)
summary(mod2)
extra.top.left.logxy("a",2,1.2)

#Figure 2. Scaling of accessory costs versus weight of embryo + endosperm, by species
```{r}
win.metafile("figs2/Accessory_Costs/Figure02_embryo_size_acc_cost_correlations.wmf", height=9, width=10)
plot

par(mfrow=c(2,2), cex=1, omi=c(1,.1,.05,.05), mai=c(.2,.8,.1,.05)) 
options(scipen = 5)

plot((scaled_seed_count)~(embryo_endo_size),SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.002,500),ylim=c(1e-4,1000),yaxt="n",xaxt="n",ylab="")
points(scaled_bud_count~embryo_endo_size,SummaryInd,pch=21,col=col.spp(species))
#points(scaled_failure_count~embryo_endo_size,SummaryInd,pch=2,col=col.spp(species))
axis(2, at=c(0.0001,0.01,1,100), labels=c(0.0001,0.01,1,100),cex.axis=1)
axis(1, at=c(0.01,1,100), labels=c("","",""),cex.axis=1)
mtext("count, scaled to plant size",2,line=2.3)
mod1 <- sma(scaled_seed_count~embryo_endo_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="OLS")
mod2 <- sma(scaled_bud_count~embryo_endo_size,data=subset(SummaryInd,scaled_bud_count!=0),log="xy",slope=-1,method="OLS")
mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")

extra.top.left.logxy("a",2,1.2)

plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.002,500),ylim=c(.004,.6),cex=1.5,xaxt="n",xlab="",ylab="")
mod <- sma(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy", method="OLS")
y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
#text((10^(0.99*(par("usr")[2]-par("usr")[1])+par("usr")[1])),(10^(0.97*(par("usr")[4]-par("usr")[3])+par("usr")[3])),paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
axis(1, at=c(0.01,1,100), labels=c("","",""),cex.axis=1)
mtext("seed set",2,line=2.3)
extra.top.left.logxy("b",2,1.2)

plot(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
mod <- sma(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="OLS")
#abline(mod$groupsummary["Int"][[1]],1,lty=2)
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=1)
mtext("pollen attraction costs (mg/seed)",2,line=2.3)
line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
line_function_log_xy_zero(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
extra.top.left.logxy("c",2,1.2)

plot(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_all_per_seed,SummarySpp[["se"]]$prepollen_costs)
mod <- sma(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="OLS")
line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
line_function_log_xy_zero(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=1)
mtext("provisioning costs (mg/seed)",2,line=2.3)
extra.top.left.logxy("d",2,1.2)
